% Registered before the corresponding data was gathered; the public commit
% history of this file is the receipt (cited by date in Methodology).
% Quantities measured later bind to the decision rules stated here.
\section{Registered hypotheses}
\label{sec:hypotheses}

Three questions in this work are decision-grade: their answers change what
the consuming inference project builds next. Each is registered here ---
hypothesis, operationalisation, predictions, decision rule --- before the
corresponding data is gathered, with this repository's commit history as
the receipt. The remaining verification gates in the paper are ordinary
methodology checks and are deliberately not elevated to this status.

\subsection{Issue-coupled costs and differential projection}
\label{sec:hyp-coupling}

This hypothesis was formed after the pipe-binding measurements (which
placed \texttt{IDP.4A} on the fma pipe, contending with FFMA issue slots)
and is registered before any differential-projection data exists.

\emph{Projected cost deltas between kernel variants that shift work onto a
contended issue pipe carry larger projection error than deltas that shift
the same work onto an uncontended pipe; under a purely additive cost model
the excess swallows the flash-attention variant-arbitration margin.}

Operationalisation: one synthetic base kernel; graded injections of FFMA
and \texttt{IDP.4A} (fma pipe, contended), \texttt{LOP3} (alu pipe,
uncontended at the operating point), and \texttt{POPC} (separate
quarter-rate unit); injection sizes chosen so true deltas land in the
5--25\% band, the arbitration operating range. Two cost models are
compared: \emph{naive additive} (op count \(\times\) reciprocal
throughput, summed) and \emph{per-pipe max} (per-pipe issue demand,
maximum across pipes, capped at the 4-per-SM-cycle issue rate).

Registered predictions: (i) additive-model differential error is larger
for fma-pipe injections than for alu-pipe injections; (ii) the per-pipe-max
model removes most of that excess; (iii) given (ii), the per-pipe-max
differential error bound discriminates deltas of 10\% and above.

Decision rule: the flash-attention variant arbitration proceeds by
projection only if the measured per-pipe-max differential error bound is
below the projected inter-variant delta; otherwise the projection route is
abandoned for that decision and both variants are implemented and measured.

\subsection{A hand-rolled NVLink exchange against the NCCL call floor}
\label{sec:hyp-exchange}

Registered before any interconnect measurement exists.

\emph{A peer-store-plus-fence exchange primitive over NVLink completes a
two-GPU exchange of at most 20\,KiB in less than half the steady-state
NCCL all-reduce per-call time at the same size.}

Operationalisation: the primitive is a peer \texttt{STG},
\texttt{\_\_threadfence\_system()}, and a system-scope flag poll, measured
end-to-end and litmus-tested for correctness (message passing with a data
check). The comparator is a two-rank NCCL all-reduce over 4--64\,KiB with
\texttt{NCCL\_ALGO}, \texttt{NCCL\_PROTO}, and channel count pinned and
recorded, taken at steady state (cold-channel rows are separate). Before
the comparison is made, a composed prediction of the primitive's round
trip from its constituent table rows (peer-store latency, fence cost, poll
read) must agree with the end-to-end measurement within a stated tolerance
--- the interconnect analogue of the projection gate.

Decision rule: the deterministic peer-exchange mechanism in the consuming
project proceeds only if the validated primitive beats half the freshly
re-measured NCCL per-call floor at 20\,KiB and below; otherwise the
mechanism is recorded as not viable on this fabric.

\subsection{Dispatch-cost composition and the decode ceiling}
\label{sec:hyp-dispatch}

Registered before any launch-family measurement exists.

\emph{The launch-family rows (empty-kernel dispatch, graph-node replay,
event costs) compose to predict the per-token host dispatch overhead of a
production-shaped decode graph within \(\pm20\%\), and the graph-replay
rows predict the decode-rate ceiling that full capture would unlock.}

Operationalisation: per-token dispatch overhead is node count
\(\times\) the relevant per-node row, compared against a profiler baseline
measured freshly on the same host and driver --- prior-session anchors are
re-measured, never reused. The ceiling prediction divides measured compute
time by the sum of compute time and predicted captured dispatch time.

Decision rule: the consuming project's capture work is prioritised by the
predicted ceiling; a composed prediction outside \(\pm20\%\) blocks the
use of these rows for that prioritisation and is published as a model
failure.

\subsection{Outcomes}
\label{sec:hypotheses-outcomes}

Recorded after the data, against the rules as registered.

\emph{Issue coupling} (\cref{sec:hyp-coupling}): prediction (i) was
confirmed --- additive-model differential error is larger for fma-pipe
injections than alu-pipe ones --- but prediction (ii) was refuted on its
registered metric, because the additive model is so uniformly poor
(93--480\% differential error) that its between-pipe gap is small; the
per-pipe-max model shows the coupling structure instead, with 3--5\%
differential error on uncontended injections against 21--28\% on
fma-coupled ones. Prediction (iii) failed: the bound does not
discriminate 10\% deltas. The decision rule then fired on the real pair:
the projection put the dp4a attention variant at $-3.9\%$ where
measurement says $+18.9\%$ --- the wrong sign, because both variants
project issue-bound while reality charges the fma-pipe coupling --- and
that variant's arbitration fell back to implement-and-measure as
registered. The staged variant's projection, by contrast, landed within
5\% of measurement (a single resource, shared memory, binds it), and
projection arbitrates that branch.

\emph{The NVLink exchange} (\cref{sec:hyp-exchange}): \textbf{confirmed
across the registered domain}, in three documented steps. The composed
gate passed flag-only ($-14\%$) and failed with payload, because the
registered composition charged the payload at streaming bandwidth a
single warp cannot reach --- the same floor-row failure mode as the
dispatch hypothesis below, observed independently. With the constituents
re-measured at the right width (a single-warp store burst and a
single-warp consumption row), the remediated gate passed at 4~KiB
($-10\%$) but still under-predicted 20~KiB by 28\%; the residual was
named --- a first-read-after-peer-write visibility cost with no table
row --- and the comparison stayed blocked there until the row existed.
Measured by its own instrument (the responder times only its read
section), the visibility row puts the first read of 20~KiB of freshly
peer-written lines at 2.59~\textmu s against 1.14 steady-state, and the
visibility-aware composition closes the gate at both sizes ($-4.5\%$ at
4~KiB, $-10.3\%$ at 20). The registered comparison therefore applies
across its stated domain: 4.92~\textmu s against a bar of 10.78 at
4~KiB (margin 2.2$\times$), 7.94 against 12.51 at 20~KiB (margin
1.6$\times$).

\emph{Dispatch composition} (\cref{sec:hyp-dispatch}): refuted. A
production-shaped decode dispatches 4{,}614 kernels per token; composed
against the empty-launch row this predicts 7.2~ms of per-token dispatch
against 14.9~ms measured ($-52\%$). The empty-launch row is a floor:
in-situ launches average 3.13~\textmu s against the row's 1.56, and four
candidate mechanisms for the gap --- argument marshalling, kernel-identity
variety, cross-device alternation, and submission-queue backpressure ---
were each measured and exonerated, leaving driver-state interaction as
the documented residual. Per the registered rule the rows are barred
from driving the capture prioritisation, which instead takes the direct
measurement: a 29.9\% launch share at this shape, and a graph-replay row
(0.91~\textmu s per node, 42\% below eager) bracketing the capture
uplift at $+15$ to $+27\%$.

One sentence of synthesis the three outcomes share: \emph{primitive rows
are floors, and composition is trustworthy exactly where one resource
binds}. The registration discipline did not make the models better; it
made their failures unignorable, cheap to localise, and safe to publish.
