\section{Conclusion}
\label{sec:conclusion}

\emph{Can a table of independently measured primitive costs predict the
behaviour of real composite kernels well enough to drive engineering
decisions?} Where a single resource binds, yes, and tightly: the
per-pipe-max projection sits within 3.5\% on every single-resource
anchor, the smem-bound attention variant within 5\%, the exchange
primitive within 4--14\% once its constituents are measured at the
right width and freshness. Where work couples across issue
pipes, or where a primitive row is a floor rather than a typical cost,
no --- and both failure modes were caught by pre-registered gates rather
than discovered in production. The practical reading for anyone pricing
similar hardware: trust the table's rows, trust compositions in
single-resource regimes, and measure directly anywhere pipes couple.

\subsection{Limitations}

One rig, one toolchain-and-driver snapshot, and rows therefore
confounded with both: a different \texttt{nvcc} emits different SASS for
the same PTX (this paper catalogues eight distinct rewrites), and a
different driver may move the host-domain rows. T4 priors transfer only
core-domain, as recorded per row. Some rows carry an honest \texttt{UNVERIFIED} flag ---
chiefly spread flags on host-domain and refresh-sensitive quantities,
where the flag is the documentation; the open remainder of the coverage
manifest is down to the store-path rows and the copy-engine transfer
curve. The chain-method atomics
offset shows that even agreeing contention structure can ride a method
constant --- though a stall-attribution profile now places that constant
in the return-value wait, where the chain interpretation put it. No independent replication exists yet. Within this rig every
SM-domain row is replicated across the two physical boards as a
publication gate, which catches die-level variation but not method or
toolchain artefacts; replication on another TU102 is a documented
one-evening procedure (\texttt{REPRODUCING.md} in the repository), and
the append-only results layout accepts additional datasets without
touching the reference one.

\subsection{Future work}

The named rows above; a width-aware launch row that would let the
dispatch composition bind; and the same table for the second
architecture this rig's market segment offers cheaply, GA102.
